Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-10 ms.tex
cleaning up text in conclusions section

Imperfect zodi corrections represent a second major limitation of our results.
The prominence of the ecliptic plane in our 
full-sky temperature map of Figure \ref{fig:results} suggests that zodiacal
light subtractions performed on the input maps are not ideal. Our comparisons 
of the maps used in this study against HI emission bear out this notion, and 
show that the imperfect zodi corrections are not limited to \verb|i100| (the
highest frequency for which the zodi should be most problematic), but in fact
are noticeable in all of the HFI ZodiCorrected maps as well. We deemed it 
infeasible to reconsider all of the \PLANCK~zodi corrections in addition to the
3000 GHz zodi correction as a part of this study. Perhaps the forthcoming 
\PLANCK~data release, including data from additional orbits, will effectively 
eliminate any residual zodi problems in the \PLANCK~bands. Under these 
circumstances it might then be worthwhile to consider revising the DIRBE 
100$\mu$m zodi correction provided by SFD.

Irrespective of the notable imperfections in our results, more detailed
comparisons between our reddening estimates here and those of SFD are required 
to determine/quantify which map is superior in particular applications. One 
definitive improvement of our reddening estimates relative to those of SFD is 
our ability to quote reddening uncertainties, which results from the 
probabilistic framework of $\S$\ref{sec:mcmc}. The extinction estimates 
from this work can also be employed as an alternative to those of SFD, to gauge
the impact of dust map choice in a specific application.

>>>>

Imperfect zodi corrections represent a second major limitation of our results.
The ecliptic plane's prominence in our full-sky temperature map (Figure 
\ref{fig:results}) suggests that the zodiacal light subtractions performed on 
the input maps are not ideal. Our comparisons of the FIR maps used in this 
study against H\,\textsc{i} emission bear out this notion, further revealing 
that the imperfect zodi corrections are not limited to \verb|i100| (the 
map for which one would expect zodiacal contamination to be most 
problematic), but in fact are noticeable in all of the HFI 
\verb|R1.10_nominal_ZodiCorrected| maps as well. We deemed it infeasible to 
reconsider all of the \PLANCK~zodi corrections in addition to the 3000 GHz zodi
correction as a part of this study. Perhaps the forthcoming \PLANCK~data 
release, including observations acquired during additional orbits, will 
effectively eliminate any residual zodi problems in the \PLANCK~bands. Under 
these circumstances it might then be worthwhile to consider revising the DIRBE 
100$\mu$m zodi correction provided by SFD.

% audit for word ``zodi'' ... is this an acceptable jargon term ?
% could use IPD as an abbreviation at certain points, not sure if i've 
% defined that acronym already somewhere else in the text?

Irrespective of the notable imperfections in our results, more detailed
comparisons between our reddening estimates here and those of SFD are required 
to determine/quantify which map is superior in particular applications. One 
definitive improvement of our reddening estimates relative to those of SFD is 
our ability to quote reddening uncertainties, which results from the 
probabilistic framework of $\S$\ref{sec:mcmc}. The extinction estimates 
from this work can also be employed as an alternative to those of SFD, to gauge
the impact of dust map choice in a specific end user's application.
